---
title: "Aida Spotify Data"
output: html_notebook
---

 

```{r setup, warning=FALSE, message=FALSE, include=FALSE}
packages.used=as.list(
  c("dplyr",
    "spotifyr",
    "plotly",
    "httpuv",
    "rbind",
    "tidy",
    "ggplot2")
)

check.pkg = function(x){
  if(!require(x, character.only=T)) install.packages(x, 
                                                     character.only=T,
                                                     dependence=T)
}
lapply(packages.used, check.pkg)

```

The first time I heard the Aida soundtrack I was maybe in 5th or 6th grade. Even then the original cast recording was older than me. At the time I had a dream of stardom, hopping from community theater show to community theater show. I couldn’t sing (still can’t) but you would never have guessed from the smiley curly haired dork under enunciation in the chorus. I bought the CD in order to rehearse at home, but it never made it out of the car. At my earliest convenience I downloaded the CD into the jukebox on the White ford escape and listened to it on loop for the duration of 3 month production and a long time after. . 

The music made me feel grown up. In part, because I remember I was the second youngest cast member, so rehearsals were basically more watching the tall teenagers in awe. The bigger reason was my mom loved that soundtrack. She always said that she got to see the show on Broadway with her mom, on of the night the great Elton John, the musical’s composer, was playing the piano. I was in that darling phase where I wanted to be just like their mother, being in Aida, listening to the music she loved, meant one step closer to becoming like her.  

As with so many childhood phases, It was a phase. My obsession with my mother quickly turned ‘lame.’ I had entered a new phase (arguably one I’m still in, but adknowlowling that is half the battle). When my mom would play the soundtrack in her car, I would roll my eyes and grown; “Mom we’ve heard this a million times” “I wanna listen to my music” [insert countless other angsty teen soundbytes]. 

Eventually my mom stopped trying to play the soundtrack, and I forgot about it. That's until this Fall when my mom’s mom passed away. 

I jet back home for the weekend of the funeral, and in the car leaving the family hour, my mom plays the Aida Soundtrack. “Grandma and I used to listen to this in the car,” she announces firmly, anticipating our disdain. The rest of us glance around, chuckles to cut the awkwardness and try to make conversation, but eventually it falls silent to the hum of the music in the background. When “How I know you” switches to “My Strongest Suit.”  I started to sing along, failed to remember most of the words, so proceeded in mumbling and stumbling through the song.  

My mom joined me in mumbling along. “This was grandma’s favorite,” she interjects during the dance break. That's not surprising. She was the most fashion forward person I knew, and as the song says, “not to strut your stuff outrageously is a crime” Hearing those lyrics again, I wouldn’t have been surprised if she helped Elton write the song. This also was my favorite song on the soundtrack. When I was in the community theater show, this was the song I gotta wear orange lipstick—talk about feeling grown up. 

But this time hearing the soundtrack I didn’t feel grown up. I felt warm, comforted, like being held in a nostalgic blanket. With me under that blanket was my mom and her mom, and they both felt closer than they had in a while. 

What had begun is a slight obsession with the soundtrack. 

To explore this obsession, let's use spotify data

```{r make token, include=FALSE}
id <- 'a748b3ec8c3c4e64a403fdea99a8844e'
secret <- '4520f0162ac04fcaa082ddd260649b45'
Sys.setenv(SPOTIFY_CLIENT_ID = id)
Sys.setenv(SPOTIFY_CLIENT_SECRET = secret)
access_token <- get_spotify_access_token()
#BQCjIJWpjMfS4Af2RgksAkFI-9Cm7gYxJft7W7rmlFrQxCKvslYi08U-f_TNGbyNPMZUS6EZ-AtrAZXbyyY
```

Okay lets see my the most recent plays of Aida. 

```{r}

# Fun fact! Its impossible to pull more than the past 50 most recently played track :(
# my_recents <- get_my_recently_played(20)
# 
# date_curr <- as.numeric(as.POSIXct(my_recents[20,1]))
# 
# cuttoff <- 1612953623 #today a year ago
# 
# while(date_curr>cuttoff){
#   temp <- get_my_recently_played(20, before=date_curr)
#   my_recents <- rbind(my_recents, temp)
#   date_till <- as.numeric(as.POSIXct(temp[20,1]))
#   
# }


```


Okay so that's literally impossible. BUT I have options. 

The Funeral was about 6 months ago. That is the exact cuttoff for what spotify considers "mid-term' when acessing my top tracks. So lets see what my top tracks are in the last 4 weeks, 6 months, and compare that my lifetime top tracks. 

```{r}
STracks <- get_my_top_artists_or_tracks(50, type = "tracks", time_range = "short_term") %>%
     mutate(range = "short") %>%
     mutate(rangenum = 1) %>%
     mutate(rank = row_number())

MTracks <- get_my_top_artists_or_tracks(50, type = "tracks", time_range = "medium_term") %>%
     mutate(range = "mid") %>%
     mutate(rangenum = 2) %>%
     mutate(rank = row_number())

LTracks<- get_my_top_artists_or_tracks(50, type = "tracks", time_range = "long_term") %>%
     mutate(range = "long") %>%
     mutate(rangenum = 3) %>%
     mutate(rank = row_number())

toptracks <- list(STracks, MTracks, LTracks)

```

For the sake of conversation lets also look at my top artists. 

```{r}
Sartists <- get_my_top_artists_or_tracks(50, type = "artists", time_range = "short_term")  %>%
     mutate(range = "short") %>%
     mutate(rangenum = 1) %>%
     mutate(rank = row_number())

Martists <- get_my_top_artists_or_tracks(50, type = "artists", time_range = "medium_term") %>%
     mutate(range = "mid") %>%
     mutate(rangenum = 2) %>%
     mutate(rank = row_number())

Lartists<- get_my_top_artists_or_tracks(50, type = "artists", time_range = "long_term") %>%
     mutate(range = "long") %>%
     mutate(rangenum = 3) %>%
     mutate(rank = row_number())

topartists <- list(Sartists, Martists, Lartists)

```

From here lets remove some unneeded of the specific data and bind them together
```{r}
#Some other day you can figure out how to do this in a loop. Its not today
# add_rank <- function(x){
#    x<- x %>%
#      mutate(rank = row_number())
# }
# 
# # i=1 # 1= short term, 2=midterm, 3=longterm
# # 
# # for (x in toptracks){
# #    x<- x %>%
# #      mutate(rank = row_number()) %>%
# #      mutate(range = i)
# #    i <- 1+i
# # }
# 
# lapply(toptracks, add_rank)


#tracks

allTopTracks <- do.call('rbind', toptracks)

allTopTracks <- allTopTracks  %>%
  select(name, album.name, range, rangenum, rank)

#albums

allTopArtists <- do.call('rbind', topartists)

allTopArtists <- allTopArtists  %>%
  select(name, range, rangenum, rank)

```

To show you how Aida Entered my life 6 months ago, lets make a bump chart

```{r}
ggplot(allTopTracks, aes(x = rangenum, y = rank, group = name)) +
  geom_line(aes(alpha = 1), size = 2) +
  #geom_point(aes(color = team, alpha = 1), size = 4) +
  scale_y_reverse(breaks = 1:nrow(allTopTracks))
```


```{r}
ggplot(allTopArtists, aes(x = rangenum, y = rank, group = name)) +
  geom_line(aes(alpha = 1), size = 2) +
  geom_point(aes(color = team, alpha = 1), size = 4) +
  scale_y_reverse(breaks = 1:nrow(allTopTracks))
```

hummm thats kinda messy... maybe we just make a table
```{r}
spreadartists <- allTopArtists %>% select(name, range, rank) %>% spread(range, name)

write.csv(spreadartists, "results/artists.csv", row.names = FALSE)

```



```{r}
allTopTracks %>%                               # Replacing values
  mutate(album.name = replace(album.name, album.name != "Aida", "Not Aida")) %>%
  ggplot(aes(x = rangenum, y = rank, group = name)) +
  geom_line(aes(color = album.name, alpha=1), size = 2) +
  geom_point(aes(color = album.name), size = 4) +
  scale_y_reverse(breaks = 1:nrow(allTopTracks))
  
```

